# avidaR

avidaR is an R package for working with data sets generated by the
[Avida](http://avida.devosoft.org/) digital evolution platform.

# Installation

The latest and greatest version of avidaR (as well as older versions) can be
installed using
[devtools](http://cran.r-project.org/web/packages/devtools/index.html):

```{r installing avidaR,eval=FALSE}
install.packages('devtools')
library(devtools)
install_github('briandconnelly/avidaR')
```

You'll also need the [stringr](https://github.com/hadley/stringr) package:

```{r installing stringr,eval=FALSE}
install.packages('stringr')
```    

# Functions

You'll first need to load avidaR:

```{r loading the avidaR package}
library(avidaR)
```

## read.avida

`read.avida` allows you to import Avida data files directly into R. The result
is a data frame. Column names for the data frame are extracted from the data
file.

```{r reading a data file}
mydata <- read.avida('time.dat')
head(mydata)
```    

Files compressed with bzip2 or gzip are automatically decompressed when loaded:

```{r reading a compressed file,eval=FALSE}
mydata <- read.avida('resource.dat.gz')
```